---
title: "auto-motion test"
author: "Dani Cosme"
date: "10/30/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.path='Figs/')
```

# load packages
```{r}
library(tidyverse)
```

# load coded data
```{r}
coded = read.csv("~/Documents/code/dsnlab/automotion-test-set/tds_artifact_coded_volumes.csv")
```

# load stripe detection data
```{r}
fileDir = "~/Documents/code/dsnlab/automotion-test-set/output/"
filePattern = "tds_stripes_.*.csv"
  
file_list = list.files(fileDir, pattern = filePattern)

for (file in file_list){
  # if the merged dataset doesn't exist, create it
  if (!exists("stripes")){
    temp = read.csv(paste0(fileDir,file))
    stripes = data.frame(temp) %>% 
      rename("volume" = t,
             "subjectID" = subject) %>%
      select(-file)
    rm(temp)
  }
  
  # if the merged dataset does exist, append to it
  else {
    temp_dataset = read.csv(paste0(fileDir,file))
    temp_dataset = data.frame(temp_dataset) %>% 
      rename("volume" = t,
             "subjectID" = subject) %>%
      select(-file)
    stripes = rbind(stripes, temp_dataset)
    rm(temp_dataset)
  }
}
```

# load global intensities and rps
```{r}
# define paths and variables
rpDir = '~/Documents/code/dsnlab/automotion-test-set/rp_txt/'
outputDir = '~/Documents/code/tds_auto-motion/auto-motion-output/'
plotDir = '~/Documents/code/tds_auto-motion/auto-motion-output/plots/'
study = "tds2"
rpPattern = "^rp_([0-9]{3})_(.*).txt"
rpCols = c("euclidian_trans","euclidian_rot","euclidian_trans_deriv","euclidian_rot_deriv","trash.rp")

# global intensities
intensities = read.csv(paste0(outputDir,study,'_globalIntensities.csv'))

# edit volume numbers for subject 157, stop3
intensities = intensities %>% 
  mutate(volume = ifelse(subjectID == 157 & run == "stop3" & volume > 43, volume - 1, volume))

# rp files
file_list = list.files(rpDir, pattern = rpPattern)

for (file in file_list){
  # if the merged dataset doesn't exist, create it
  if (!exists("rp")){
    temp = read.table(paste0(rpDir,file))
    colnames(temp) = rpCols
    rp = data.frame(temp, file = rep(file,count(temp))) %>% 
      mutate(volume = row_number()) %>%
      extract(file,c("subjectID","run"), rpPattern) %>%
      mutate(subjectID = as.integer(subjectID))
    rm(temp)
  }
  
  # if the merged dataset does exist, append to it
  else {
    temp_dataset = read.table(paste0(rpDir,file))
    colnames(temp_dataset) = rpCols
    temp_dataset = data.frame(temp_dataset, file = rep(file,count(temp_dataset))) %>% 
      mutate(volume = row_number()) %>%
      extract(file,c("subjectID","run"), rpPattern) %>%
      mutate(subjectID = as.integer(subjectID))
    rp = rbind(rp, temp_dataset)
    rm(temp_dataset)
  }
}
```

# join dataframes
```{r}
joined = left_join(stripes, coded, by = c("subjectID", "run", "volume")) %>%
  left_join(., intensities, by = c("subjectID", "run", "volume")) %>%
  left_join(., rp, by = c("subjectID", "run", "volume")) %>%
  mutate(striping = ifelse(is.na(striping), 0, striping),
         intensity = ifelse(is.na(intensity), 0, intensity))
```

# apply intensity and rp thresholds
```{r}
auto = joined %>%
  group_by(subjectID, run) %>%
  mutate(Diff.mean = volMean - lag(volMean),
         Diff.sd = volSD - lag(volSD)) %>%
  filter(tile == 1 | tile == 10) %>%
  ungroup %>%
  mutate(meanDiff.mean = mean(Diff.mean, na.rm=TRUE),
         sdDiff.mean = sd(Diff.mean, na.rm=TRUE),
         meanDiff.sd = mean(Diff.sd, na.rm=TRUE),
         sdDiff.sd = sd(Diff.sd, na.rm=TRUE),
         
         # code volumes above mean thresholds as trash
         trash.mean = ifelse(Diff.mean > (meanDiff.mean + 3*sdDiff.mean) | Diff.mean < (meanDiff.mean - 1.5*sdDiff.mean), 1, 0),
         trash.sd = ifelse(Diff.sd > (meanDiff.sd + 3*sdDiff.sd) | Diff.sd < (meanDiff.sd - 3*sdDiff.sd), 1, 0),
         
         # code volumes with more than +/- .3mm translation in Euclidian distance
         trash.rp = ifelse(euclidian_trans_deriv > .3 | euclidian_trans_deriv < -.3, 1, trash.rp),
         # code volumes with more than +/- .3mm translation in Euclidian distance
         trash.rp = ifelse(euclidian_rot_deriv > .3 | euclidian_rot_deriv < -.3, 1, trash.rp),
         
         # recode as trash if volume behind and in front are both marked as trash
         trash.mean = ifelse(trash.mean == 0 & lag(trash.mean) == 1 & lead(trash.mean) == 1, 1, trash.mean),
         trash.sd = ifelse(trash.sd == 0 & lag(trash.sd) == 1 & lead(trash.sd) == 1, 1, trash.sd),
         trash.rp = ifelse(trash.rp == 0 & lag(trash.rp) == 1 & lead(trash.rp) == 1, 1, trash.rp),
         
         # code first volume as trash if second volume is trash
         trash.mean = ifelse(volume == 1 & lead(trash.mean) == 1, 1, trash.mean),
         trash.sd = ifelse(volume == 1 & lead(trash.sd) == 1, 1, trash.sd),
         trash.rp = ifelse(volume == 1 & lead(trash.rp) == 1, 1, trash.rp)) %>%
  
  mutate(trash.mean = ifelse(is.na(trash.mean), 0, trash.mean),
         trash.sd = ifelse(is.na(trash.sd), 0, trash.sd),
         hits.rp = ifelse(trash.rp == 1 & (striping == 2 | intensity == 2), "hit",
                ifelse(trash.rp == 1 & (striping == 1 | intensity == 1), "hit.light",
                ifelse(trash.rp == 1 & (striping == 0 | intensity == 0), "pos",
                ifelse(trash.rp == 0 & (striping == 2 | intensity == 2), "neg",
                ifelse(trash.rp == 0 & (striping == 1 | intensity == 1), "neg.light", NA))))),
         hits.mean = ifelse(trash.mean == 1 & (striping == 2 | intensity == 2), "hit",
                ifelse(trash.mean == 1 & (striping == 1 | intensity == 1), "hit.light",
                ifelse(trash.mean == 1 & (striping == 0 | intensity == 0), "pos",
                ifelse(trash.mean == 0 & (striping == 2 | intensity == 2), "neg",
                ifelse(trash.mean == 0 & (striping == 1 | intensity == 1), "neg.light", NA))))),
         hits.sd = ifelse(trash.sd == 1 & (striping == 2 | intensity == 2), "hit",
                ifelse(trash.sd == 1 & (striping == 1 | intensity == 1), "hit.light",
                ifelse(trash.sd == 1 & (striping == 0 | intensity == 0), "pos",
                ifelse(trash.sd == 0 & (striping == 2 | intensity == 2), "neg",
                ifelse(trash.sd == 0 & (striping == 1 | intensity == 1), "neg.light", NA))))),
         label = ifelse(regexpr(".*", hits.rp) | regexpr(".*", hits.mean) | regexpr(".*", hits.sd), as.character(volume), '')) %>%
  select(subjectID, run, volume, Diff.mean, Diff.sd, volMean, volSD, starts_with("euclidian"), hits.mean, hits.sd, hits.rp, tile, label)

```

# plot mean intensities
```{r auto-mean, fig.width=20, fig.height=100}
ggplot(filter(auto, tile == 1), aes(x = volume, y = volMean)) +
  geom_line(size = .25) +
  geom_point(data = subset(auto, !is.na(hits.mean)), aes(color = hits.mean), size = 2.5) +
  geom_text(aes(label = label), size = 2, position = position_nudge(x = 1.5, y = .000025)) +
  facet_wrap(~ subjectID + run, ncol = 4, scales = "free") +
  scale_color_manual(values = c("#3B9AB2","#78B7C5","#9EBE91","#EBCC2A","#F21A00")) +
  #geom_hline(data = thresholds, aes(yintercept = upper), color = "#F21A00") +
  #geom_hline(data = thresholds, aes(yintercept = lower), color = "#F21A00") +
  theme(axis.text.x = element_text(size = 6))
```

# plot sd intensities
```{r auto-sd, fig.width=20, fig.height=100}
ggplot(filter(auto, tile == 1), aes(x = volume, y = volSD)) +
  geom_line(size = .25) +
  geom_point(data = subset(auto, !is.na(hits.sd)), aes(color = hits.sd), size = 2.5) +
  geom_text(aes(label = label), size = 2, position = position_nudge(x = 1.5, y = .000025)) +
  facet_wrap(~ subjectID + run, ncol = 4, scales = "free") +
  scale_color_manual(values = c("#3B9AB2","#78B7C5","#9EBE91","#EBCC2A","#F21A00")) +
  #geom_hline(data = thresholds, aes(yintercept = upper), color = "#F21A00") +
  #geom_hline(data = thresholds, aes(yintercept = lower), color = "#F21A00") +
  theme(axis.text.x = element_text(size = 6))
```

# plot translation
```{r auto-translation, fig.width=20, fig.height=100}
ggplot(filter(auto, tile == 1), aes(x = volume, y = euclidian_trans_deriv)) +
  geom_line(size = .25) +
  geom_point(data = subset(auto, !is.na(hits.rp)), aes(color = hits.rp), size = 2.5) +
  geom_text(aes(label = label), size = 2, position = position_nudge(x = 1.5, y = .000025)) +
  facet_wrap(~ subjectID + run, ncol = 4, scales = "free") +
  scale_color_manual(values = c("#3B9AB2","#78B7C5","#9EBE91","#EBCC2A","#F21A00")) +
  #geom_hline(data = thresholds, aes(yintercept = upper), color = "#F21A00") +
  #geom_hline(data = thresholds, aes(yintercept = lower), color = "#F21A00") +
  theme(axis.text.x = element_text(size = 6))
```

# apply absolute thresholds and plot
```{r stripe-absolute, fig.width=20, fig.height=100}
test = joined %>%
  group_by(subjectID, run, tile) %>%
  mutate(freqtile_power_c = freqtile_power - mean(freqtile_power)) %>%
  ungroup() %>%
  filter(tile == 1 | tile == 10) %>%
  select(-freqtile_power) %>%
  spread(tile,freqtile_power_c) %>%
  mutate(red_zone = ifelse(`1` < -.03 & `10` > .0002, TRUE, FALSE),
         red_zone = ifelse(lead(red_zone) == TRUE, TRUE, red_zone),
         hits = ifelse(red_zone == TRUE & (striping == 2 | intensity == 2), "hit",
                ifelse(red_zone == TRUE & (striping == 1 | intensity == 1), "hit.light",
                ifelse(red_zone == TRUE & (striping == 0 | intensity == 0), "pos",
                ifelse(red_zone == FALSE & (striping == 2 | intensity == 2), "neg",
                ifelse(red_zone == FALSE & (striping == 1 | intensity == 1), "neg.light", NA))))),
         label = ifelse(hits, as.character(volume), ''),
         hits = as.factor(hits)) %>%
  gather(tile, freqtile_power_c, c(`1`, `10`)) %>%
  mutate(tile = as.numeric(tile))

thresholds = test %>% select(subjectID, run, tile) %>% unique(.) %>% mutate(y = ifelse(tile == 1, -.03, .00025))

ggplot(test, aes(x = volume, y = freqtile_power_c)) +
  geom_line(size = .25) +
  geom_point(data = subset(test, !is.na(hits)), aes(color = hits), size = 2.5) +
  geom_text(aes(label = label), size = 2, position = position_nudge(x = 1.5, y = .000025)) +
  facet_wrap(~subjectID + run + tile, scales = "free", ncol = 4) +
  scale_color_manual(values = c("#3B9AB2","#78B7C5","#9EBE91","#EBCC2A","#F21A00")) +
  geom_hline(data = thresholds, aes(yintercept = y), color = "#F21A00") +
  theme(axis.text.x = element_text(size = 6))
```

# apply threshold using SDs and plot
```{r stripe-diff, fig.width=20, fig.height=100}
test_diff = joined %>%
  group_by(subjectID, run, tile) %>%
  mutate(freqtile_power_c = freqtile_power - mean(freqtile_power),
         diff = freqtile_power - lag(freqtile_power)) %>%
  select(-freqtile_power, -freqtile_power_c) %>%
  filter(tile == 1 | tile == 10) %>%
  spread(tile,diff) %>%
  ungroup() %>%
  mutate(upper_1 = (mean(`1`,na.rm=TRUE) + 1.25*sd(`1`, na.rm=TRUE)),
         lower_1 = (mean(`1`,na.rm=TRUE) - 1.25*sd(`1`, na.rm=TRUE)),
         upper_10 = (mean(`10`,na.rm=TRUE) + 1.25*sd(`10`, na.rm=TRUE)),
         lower_10 = (mean(`10`,na.rm=TRUE) - 1.25*sd(`10`, na.rm=TRUE))) %>%
  mutate(red_zone_1 = ifelse(`1` > upper_1 | `1` < lower_1, TRUE, FALSE),
         red_zone_10 = ifelse(`10` > upper_10 | `10` < lower_10, TRUE, FALSE),
         red_zone = ifelse(red_zone_1 == TRUE & red_zone_10 == TRUE, TRUE, FALSE),
         red_zone = ifelse(lead(red_zone) == TRUE, TRUE, red_zone),
         red_zone = ifelse(is.na(red_zone), 0, red_zone),
         hits = ifelse(red_zone == TRUE & (striping == 2 | intensity == 2), "hit",
                ifelse(red_zone == TRUE & (striping == 1 | intensity == 1), "hit.light",
                ifelse(red_zone == TRUE & (striping == 0 | intensity == 0), "pos",
                ifelse(red_zone == FALSE & (striping == 2 | intensity == 2), "neg",
                ifelse(red_zone == FALSE & (striping == 1 | intensity == 1), "neg.light", NA))))),
         label = ifelse(hits, as.character(volume), ''),
         hits = as.factor(hits)) %>%
  gather(tile, diff, c(`1`, `10`)) %>%
  mutate(tile = as.numeric(tile))

thresholds = test_diff %>% 
  select(subjectID, run, tile, diff) %>% 
  group_by(tile) %>%
  mutate(upper = mean(diff, na.rm=TRUE) + 1*sd(diff, na.rm=TRUE),
         lower = mean(diff, na.rm=TRUE) - 1*sd(diff, na.rm=TRUE)) %>%
  select(-diff) %>%
  unique(.)

ggplot(test_diff, aes(x = volume, y = diff)) +
  geom_line(size = .25) +
  geom_point(data = subset(test_diff, !is.na(hits)), aes(color = hits), size = 2.5) +
  geom_text(aes(label = label), size = 2, position = position_nudge(x = 1.5, y = .000025)) +
  facet_wrap(~ subjectID + run + tile, ncol = 4, scales = "free") +
  scale_color_manual(values = c("#3B9AB2","#78B7C5","#9EBE91","#EBCC2A","#F21A00")) +
  geom_hline(data = thresholds, aes(yintercept = upper), color = "#F21A00") +
  geom_hline(data = thresholds, aes(yintercept = lower), color = "#F21A00") +
  theme(axis.text.x = element_text(size = 6))
```

# make composite
```{r, fig.width=20, fig.height=100}
comp = joined %>%
  filter(tile == 1 | tile == 10) %>%
  
  # code trash based on mean, sd, and rp 
  group_by(subjectID, run, tile) %>%
  mutate(Diff.mean = volMean - lag(volMean),
         Diff.sd = volSD - lag(volSD)) %>%
  ungroup %>%
  mutate(meanDiff.mean = mean(Diff.mean, na.rm=TRUE),
         sdDiff.mean = sd(Diff.mean, na.rm=TRUE),
         meanDiff.sd = mean(Diff.sd, na.rm=TRUE),
         sdDiff.sd = sd(Diff.sd, na.rm=TRUE),
         
         # code volumes above mean thresholds as trash
         trash.mean = ifelse(Diff.mean > (meanDiff.mean + 2*sdDiff.mean) | Diff.mean < (meanDiff.mean - 2*sdDiff.mean), 1, 0),
         trash.sd = ifelse(Diff.sd > (meanDiff.sd + 2*sdDiff.sd) | Diff.sd < (meanDiff.sd - 2*sdDiff.sd), 1, 0),
         
         # code volumes with more than +/- .3mm translation or in Euclidian distance
         trash.rp.tr = ifelse(euclidian_trans_deriv > .25 | euclidian_trans_deriv < -.25, 1, trash.rp),
         trash.rp.rot = ifelse(euclidian_rot_deriv > .25 | euclidian_rot_deriv < -.25, 1, trash.rp)) %>%
  select(-meanDiff.mean, -meanDiff.sd, -sdDiff.mean, -sdDiff.sd) %>%
  
  # code trash based on striping
  group_by(subjectID, run, tile) %>%
  mutate(freqtile_power_c = freqtile_power - mean(freqtile_power, na.rm=TRUE)) %>%
  ungroup() %>%
  select(-freqtile_power) %>%
  spread(tile,freqtile_power_c) %>%
  mutate(trash.stripe = ifelse(`1` < -.035 & `10` > .00025, 1, 0)) %>%
  
  # combine trash
  mutate(trash.combined = ifelse(trash.stripe == 1, 1, 0),
         trash.combined = ifelse((trash.rp.tr + trash.rp.rot + trash.mean + trash.sd) > 2, 1, trash.combined),
         #trash.combined = ifelse((trash.mean + trash.sd) == 2, 1, trash.combined),
         trash.combined = ifelse(lead(trash.combined) == TRUE, TRUE, trash.combined)) %>%
  
  # code hits
  mutate(hits = ifelse(trash.combined == 1 & (striping == 2 | intensity == 2), "hit",
                ifelse(trash.combined == 1 & (striping == 1 | intensity == 1), "hit.light",
                ifelse(trash.combined == 1 & (striping == 0 | intensity == 0), "pos",
                ifelse(trash.combined == 0 & (striping == 2 | intensity == 2), "neg",
                ifelse(trash.combined == 0 & (striping == 1 | intensity == 1), "neg.light", NA))))),
         label = ifelse(regexpr('.*', hits), as.character(volume), ''),
         hits = as.factor(hits)) %>%
  gather(tile, freqtile_power_c, c(`1`, `10`)) %>%
  mutate(tile = as.numeric(tile))
```

# plot  composite, y = translation derivative
```{r comp-translation, fig.width=20, fig.height=100}
ggplot(filter(comp, tile == 1), aes(x = volume, y = euclidian_trans_deriv)) +
  geom_line(size = .25) +
  geom_point(data = subset(comp, !is.na(hits)), aes(color = hits), size = 2.5) +
  geom_text(aes(label = label), size = 1.5) +
  facet_wrap(~ subjectID + run, ncol = 4, scales = "free") +
  scale_color_manual(values = c("#3B9AB2","#78B7C5","#9EBE91","#EBCC2A","#F21A00")) +
  theme(axis.text.x = element_text(size = 6))
```

# plot  composite, y = mean intensity
```{r comp-mean, fig.width=20, fig.height=100}
ggplot(filter(comp, tile == 1), aes(x = volume, y = volMean)) +
  geom_line(size = .25) +
  geom_point(data = subset(comp, !is.na(hits)), aes(color = hits), size = 2.5) +
  geom_text(aes(label = label), size = 1.5) +
  facet_wrap(~ subjectID + run, ncol = 4, scales = "free") +
  scale_color_manual(values = c("#3B9AB2","#78B7C5","#9EBE91","#EBCC2A","#F21A00")) +
  theme(axis.text.x = element_text(size = 6))
```

# plot  composite, y = freqtile power
```{r comp-freq, fig.width=20, fig.height=100}
ggplot(comp, aes(x = volume, y = freqtile_power_c)) +
  geom_line(size = .25) +
  geom_point(data = subset(comp, !is.na(hits)), aes(color = hits), size = 2.5) +
  geom_text(aes(label = label), size = 1.5) +
  facet_wrap(~ subjectID + run + tile, ncol = 4, scales = "free") +
  scale_color_manual(values = c("#3B9AB2","#78B7C5","#9EBE91","#EBCC2A","#F21A00")) +
  theme(axis.text.x = element_text(size = 6))
```

# compare hit rates
```{r, fig.width=20, fig.height=175}
# auto thresholding
table(auto$hits.mean)
table(auto$hits.sd)
table(auto$hits.rp)

# absolute thresholing
table(test$hits)

# SD thresholding
table(test_diff$hits)

# composite
table(comp$hits)

# hits = left_join(test, test_diff, by = c("subjectID", "run", "volume", "tile", "striping")) %>%
#   left_join(., auto, by = c("subjectID", "run", "volume", "tile")) %>%
#   select(subjectID, run, volume, tile, euclidian_trans_deriv, striping, hits.x, hits.y, hits.mean, hits.sd, hits.rp) %>%
#   rename("stripe.absolute" = hits.x,
#          "stripe.diff" = hits.y,
#          "auto.intensity.mean" = hits.mean,
#          "auto.intensity.sd" = hits.sd,
#          "auto.rp" = hits.rp) %>%
#   gather(method, hits, c("auto.intensity.mean", "auto.intensity.sd", "auto.rp", "stripe.absolute", "stripe.diff")) %>%
#   mutate(label = ifelse(regexpr('.*', hits), as.character(volume), ''))

# plot hits
# hits1 = filter(hits, tile == 1 & subjectID == 102)
# ggplot(filter(hits, tile == 1), aes(x = volume, y = euclidian_trans_deriv)) +
#   geom_line(size = .25) +
#   geom_point(data = subset(hits, !is.na(hits)), aes(color = hits), size = 2.5) +
#   geom_text(aes(label = label), size = 1.5) +
#   facet_wrap(~ subjectID + run + method, ncol = 5, scales = "free") +
#   scale_color_manual(values = c("#3B9AB2","#78B7C5","#9EBE91","#EBCC2A","#F21A00")) +
#   theme(axis.text.x = element_text(size = 6))
```
