---
title: "auto-motion test FP development"
author: "Dani Cosme"
date: "1/5/2018"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.path='Figs/FP/')
options(scipen=999)
```

# load packages
```{r}
library(tidyverse)
library(glmnet)
library(caTools)
library(caret)
library(ROCR)
```

# load coded data
```{r}
coded = read.csv("~/Documents/code/dsnlab/automotion-test-set/FP_manuallyCoded_edited2.csv") %>%
  select(subjectID, run, volume, trash) %>%
  rename("artifact" = trash)
```

# load stripe detection data
```{r}
fileDir = "~/Documents/code/dsnlab/automotion-test-set/output/FP/"
filePattern = "FP_stripes_.*.csv"
  
file_list = list.files(fileDir, pattern = filePattern)

for (file in file_list){
  # if the merged dataset doesn't exist, create it
  if (!exists("stripes")){
    temp = read.csv(paste0(fileDir,file))
    stripes = data.frame(temp) %>% 
      rename("volume" = t,
             "subjectID" = subject) %>%
      select(-file)
    rm(temp)
  }
  
  # if the merged dataset does exist, append to it
  else {
    temp_dataset = read.csv(paste0(fileDir,file))
    temp_dataset = data.frame(temp_dataset) %>% 
      rename("volume" = t,
             "subjectID" = subject) %>%
      select(-file)
    stripes = rbind(stripes, temp_dataset)
    rm(temp_dataset)
  }
}
```

# load global intensities and rps
```{r}
# define paths and variables
rpDir = '~/Documents/code/dsnlab/automotion-test-set/FP_rp_txt/'
# outputDir = '~/Documents/code/tds_auto-motion/auto-motion-output/'
# plotDir = '~/Documents/code/tds_auto-motion/auto-motion-output/plots/'
study = "FP"
rpPattern = '^rp_(FP[0-9]{3})_(.*).txt'
rpCols = c("euclidian_trans","euclidian_rot","euclidian_trans_deriv","euclidian_rot_deriv","trash.rp")

# global intensities
intensities = read.csv(paste0('~/Documents/code/dsnlab/automotion-test-set/',study,'_globalIntensities.csv'))

# rp files
file_list = list.files(rpDir, pattern = rpPattern)

for (file in file_list){
  # if the merged dataset doesn't exist, create it
  if (!exists("rp")){
    temp = read.table(paste0(rpDir,file))
    colnames(temp) = rpCols
    rp = data.frame(temp, file = rep(file,count(temp))) %>% 
      mutate(volume = row_number()) %>%
      extract(file,c("subjectID","run"), rpPattern)
    rm(temp)
  }
  
  # if the merged dataset does exist, append to it
  else {
    temp_dataset = read.table(paste0(rpDir,file))
    colnames(temp_dataset) = rpCols
    temp_dataset = data.frame(temp_dataset, file = rep(file,count(temp_dataset))) %>% 
      mutate(volume = row_number()) %>%
      extract(file,c("subjectID","run"), rpPattern)
    rp = rbind(rp, temp_dataset)
    rm(temp_dataset)
  }
}
```

# join dataframes
```{r}
joined = left_join(stripes, coded, by = c("subjectID", "run", "volume")) %>%
  left_join(., intensities, by = c("subjectID", "run", "volume")) %>%
  left_join(., rp, by = c("subjectID", "run", "volume")) %>%
  mutate(tile = paste0("tile_",tile)) %>%
  group_by(subjectID, run, tile) %>%
  mutate(Diff.mean = volMean - lag(volMean),
         Diff.sd = volSD - lag(volSD)) %>%
  spread(tile, freqtile_power)
```

# split the data 
```{r}
set.seed(101) 
sample = sample.split(joined$artifact, SplitRatio = .75)
training = subset(joined, sample == TRUE)
testing = subset(joined, sample == FALSE)
```

# machine learning
## tidy training and testing data
```{r}
train.ml = training %>%
  group_by(subjectID, run) %>%
  mutate(Diff.mean = ifelse(is.na(Diff.mean),0,Diff.mean),
         Diff.sd = ifelse(is.na(Diff.sd),0,Diff.sd)) %>%
  gather(tile,freqtile_power, starts_with("tile")) %>%
  mutate(tile = paste0(tile,"_c")) %>%
  group_by(subjectID, run, tile) %>%
  mutate(freqtile_power_c = freqtile_power - mean(freqtile_power, na.rm=TRUE)) %>%
  ungroup() %>%
  select(-freqtile_power) %>%
  spread(tile,freqtile_power_c) %>%
  select(-trash.rp, -volMean, -volSD, -euclidian_rot, -euclidian_trans) %>%
  select(subjectID, run, volume, artifact, everything())

test.ml = testing %>%
  group_by(subjectID, run) %>%
  mutate(Diff.mean = ifelse(is.na(Diff.mean),0,Diff.mean),
         Diff.sd = ifelse(is.na(Diff.sd),0,Diff.sd)) %>%
  gather(tile,freqtile_power, starts_with("tile")) %>%
  mutate(tile = paste0(tile,"_c")) %>%
  group_by(subjectID, run, tile) %>%
  mutate(freqtile_power_c = freqtile_power - mean(freqtile_power, na.rm=TRUE)) %>%
  ungroup() %>%
  select(-freqtile_power) %>%
  spread(tile,freqtile_power_c) %>%
  select(-trash.rp, -volMean, -volSD, -euclidian_rot, -euclidian_trans) %>%
  select(subjectID, run, volume, artifact, everything())
```

## use lasso logistic regression to fit beta weights for each predictor
### training
```{r, logistic-regression}
# subset predictors and criterion
x_train = as.matrix(train.ml[,-c(1,2,3,4)])
y_train = as.double(as.matrix(train.ml[, 4]))

# run xval to determine lambda
cv.train <- cv.glmnet(x_train, y_train, family='binomial', alpha=1, parallel=TRUE, standardize=TRUE, type.measure='auc')

plot(cv.train)
plot(cv.train$glmnet.fit, xvar="lambda", label=TRUE)
cv.train$lambda.min
cv.train$lambda.1se
coef(cv.train, s=cv.train$lambda.min)
coef(cv.train, s=cv.train$lambda.1se)

# test on sample
pred_train = predict(cv.train, newx = x_train, s=cv.train$lambda.1se, type="response")

# plot cutoff v. accuracy
predicted = prediction(pred_train, y_train, label.ordering = NULL)
perf = performance(predicted, measure = "acc")
perf.df = data.frame(cut=perf@x.values[[1]],acc=perf@y.values[[1]])

ggplot(perf.df, aes(cut, acc)) +
  geom_line()

# plot false v. true positive rate
perf = performance(predicted, measure = "tpr", x.measure = "fpr")
perf.df = data.frame(cut=perf@alpha.values[[1]],fpr=perf@x.values[[1]],tpr=perf@y.values[[1]])

ggplot(perf.df, aes(fpr, tpr)) +
  geom_line()

# plot specificity v. sensitivity
perf = performance(predicted, measure = "sens", x.measure = "spec")
perf.df = data.frame(cut=perf@alpha.values[[1]],sens=perf@x.values[[1]],spec=perf@y.values[[1]])
ggplot(perf.df, aes(spec, sens)) +
  geom_line()

ggplot(perf.df, aes(x = cut)) +
  geom_line(aes(y = sens, color = "sensitivity")) + 
  geom_line(aes(y = spec, color = "specificity"))

perf@alpha.values[[1]][which.max(perf@x.values[[1]]+perf@y.values[[1]])] # cut
max(perf@x.values[[1]]+perf@y.values[[1]]) # sensitivity + specificity

# confusion matrix
pred_train = predict(cv.train, newx = x_train, s=cv.train$lambda.1se, type="response")
pred_train[pred_train > .05] = 1
pred_train[pred_train < .05] = 0
confusionMatrix(pred_train, y_train)
```

### testing
```{r}
# subset predictors and criterion
x_test = as.matrix(test.ml[,-c(1,2,3,4)])
y_test = as.double(as.matrix(test.ml[, 4]))

# test on holdout sample
pred_test = predict(cv.train, newx = x_test, s=cv.train$lambda.1se, type="response")
pred_test[pred_test > .05] = 1
pred_test[pred_test < .05] = 0

# confusion matrix
confusionMatrix(pred_test, y_test)
```

## svm
### training
```{r}
train.svm = train.ml[,-c(1,2,3)] %>%
  mutate(artifact = ifelse(artifact == 1, "yes","no"),
         artifact = as.factor(artifact))

# specify control parameters
fitControl = trainControl(method = "repeatedcv", number = 10, repeats = 3, classProbs = TRUE)

# run initial model
set.seed(101)
svmFit = train(artifact ~ ., 
               data = train.svm, 
               method = "svmLinear", 
               trControl = fitControl,
               preProcess = c("center", "scale"),
               tuneLength = 10,
               metric = "ROC",
               verbose = FALSE)
svmFit$finalModel

# predict model
train_pred = predict(svmFit, newdata = train.svm, type="prob") %>%
  select(-no)

# plot cutoff v. accuracy
predicted = prediction(train_pred, train.svm$artifact, label.ordering = NULL)
perf = performance(predicted, measure = "acc")
perf.df = data.frame(cut=perf@x.values[[1]],acc=perf@y.values[[1]])

ggplot(perf.df, aes(cut, acc)) +
  geom_line()

# plot false v. true positive rate
perf = performance(predicted, measure = "tpr", x.measure = "fpr")
perf.df = data.frame(cut=perf@alpha.values[[1]],fpr=perf@x.values[[1]],tpr=perf@y.values[[1]])

ggplot(perf.df, aes(fpr, tpr)) +
  geom_line()

# plot specificity v. sensitivity
perf = performance(predicted, measure = "sens", x.measure = "spec")
perf.df = data.frame(cut=perf@alpha.values[[1]],sens=perf@x.values[[1]],spec=perf@y.values[[1]])
ggplot(perf.df, aes(spec, sens)) +
  geom_line()

ggplot(perf.df, aes(x = cut)) +
  geom_line(aes(y = sens, color = "sensitivity")) + 
  geom_line(aes(y = spec, color = "specificity"))

perf@alpha.values[[1]][which.max(perf@x.values[[1]]+perf@y.values[[1]])] # cut
max(perf@x.values[[1]]+perf@y.values[[1]]) # sensitivity + specificity

# cut and assess accuracy in training sample
train_pred = predict(svmFit, newdata = train.svm, type="prob") %>%
  select(-no)
train_pred =  as.matrix(train_pred)
train_pred[train_pred > .09] = "yes"
train_pred[train_pred < .09] = "no"
confusionMatrix(train_pred, train.svm$artifact)
```

### testing
```{r}
test.svm = test.ml[,-c(1,2,3)] %>%
  mutate(artifact = ifelse(artifact == 1, "yes","no"),
         artifact = as.factor(artifact))

# cut and assess accuracy in test sample
test_pred = predict(svmFit, newdata = test.svm, type="prob") %>%
  select(-no)
test_pred =  as.matrix(test_pred)
test_pred[test_pred > .09] = "yes"
test_pred[test_pred < .09] = "no"
confusionMatrix(test_pred, test.svm$artifact)
```

## save models
```{r}
setwd("~/Documents/code/dsnlab/automotion-test-set")
saveRDS(cv.train, "model_log_FP.rds")
saveRDS(svmFit, "model_svm_FP.rds")
```

### weighted model
```{r}
# create model weights (they sum to one)
# model_weights = ifelse(train.svm$artifact == "yes",
#                         (1/table(train.svm$artifact)[1]) * 0.5,
#                         (1/table(train.svm$artifact)[2]) * 0.5)
# 
# # use the same seed to ensure same cross-validation splits
# fitControl$seeds = svmFit$control$seeds
# 
# svmFit_weighted = train(artifact ~ .,
#                data = train.svm,
#                method = "svmLinear",
#                trControl = fitControl,
#                preProcess = c("center", "scale"),
#                tuneLength = 10,
#                metric = "ROC",
#                verbose = FALSE,
#                weights = model_weights)
# 
# svmFit_weighted$finalModel
# 
# test_pred_weighted = predict(svmFit_weighted, newdata = test.svm, type="prob") %>%
#   select(-no)
# test_pred_weighted =  as.matrix(test_pred_weighted)
# test_pred_weighted[test_pred_weighted > .07] = "yes"
# test_pred_weighted[test_pred_weighted < .07] = "no"
# confusionMatrix(test_pred_weighted, test.svm$artifact)

# # determine best cost parameter
# grid <- expand.grid(C = c(0, 0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 1, 1.25, 1.5, 1.75, 2, 5))
# set.seed(3233)
# svm_Linear_Grid <- train(artifact ~ ., 
#                          data = train.svm, method = "svmLinear",
#                          trControl=fitControl,
#                          preProcess = c("center", "scale"),
#                          tuneGrid = grid,
#                          tuneLength = 10)
# svm_Linear_Grid
# plot(svm_Linear_Grid)
# test_pred_grid = predict(svm_Linear_Grid, newdata = test.svm)
# confusionMatrix(test_pred_grid, test.svm$artifact)
```

# auto-motion process
## training
```{r, fig.width=20, fig.height=100}
train.man = training %>%
  gather(tile, freqtile_power, starts_with("tile")) %>%
  filter(tile %in% c("tile_1", "tile_10")) %>%
  
  # code trash based on mean, sd, and rp
  ungroup %>%
  mutate(meanDiff.mean = mean(Diff.mean, na.rm=TRUE),
         sdDiff.mean = sd(Diff.mean, na.rm=TRUE),
         meanDiff.sd = mean(Diff.sd, na.rm=TRUE),
         sdDiff.sd = sd(Diff.sd, na.rm=TRUE),
         
         # code volumes above mean thresholds as trash
         upper.mean = meanDiff.mean + 2*sdDiff.mean,
         lower.mean = meanDiff.mean - 2*sdDiff.mean,
         trash.mean = ifelse(Diff.mean > upper.mean | Diff.mean < lower.mean, 1, 0),
         
         upper.sd = meanDiff.sd + 2*sdDiff.sd,
         lower.sd = meanDiff.sd - 2*sdDiff.sd,
         trash.sd = ifelse(Diff.sd > upper.sd | Diff.sd < lower.sd, 1, 0),
         
         # code volumes with more than +/- .25mm translation or rotation in Euclidian distance
         trash.rp.tr = ifelse(euclidian_trans_deriv > .25 | euclidian_trans_deriv < -.25, 1, 0),
         trash.rp.rot = ifelse(euclidian_rot_deriv > .25 | euclidian_rot_deriv < -.25, 1, 0)) %>%
  select(-meanDiff.mean, -meanDiff.sd, -sdDiff.mean, -sdDiff.sd) %>%
  
  # code trash based on striping
  group_by(subjectID, run, tile) %>%
  mutate(freqtile_power_c = freqtile_power - mean(freqtile_power, na.rm=TRUE)) %>%
  ungroup() %>%
  select(-freqtile_power) %>%
  spread(tile,freqtile_power_c) %>%
  mutate(trash.stripe = ifelse(tile_1 < -.035 & tile_10 > .00025, 1, 0)) %>%
  
  # combine trash
  mutate(trash.combined = ifelse(trash.stripe == 1, 1, 0),
         trash.sum = trash.rp.tr + trash.rp.rot + trash.mean + trash.sd,
         trash.combined = ifelse((trash.rp.tr + trash.rp.rot + trash.mean + trash.sd) > 1, 1, trash.combined)) %>%

  # recode as trash if volume behind and in front are both marked as trash
  mutate(trash.combined = ifelse(trash.combined == 0 & lag(trash.combined) == 1 & lead(trash.combined) == 1, 1, trash.combined)) %>%
         
  # code first volume as trash if second volume is trash
  mutate(trash.combined = ifelse(volume == 1 & lead(trash.combined) == 1, 1, trash.combined)) %>%

  # code hits
  mutate(hits = ifelse(trash.combined == 1 & (artifact == 1), "hit",
                ifelse(trash.combined == 0 & (artifact == 1), "neg",
                ifelse(trash.combined == 1 & (artifact == 0), "pos", NA))),
         label = ifelse(regexpr('.*', hits), as.character(volume), ''),
         hits = as.factor(hits)) %>%
  gather(tile, freqtile_power_c, c("tile_1", "tile_10"))
```

## testing
```{r}
test.man = testing %>%
  gather(tile, freqtile_power, starts_with("tile")) %>%
  filter(tile %in% c("tile_1", "tile_10")) %>%
  
  # code trash based on mean, sd, and rp 
  ungroup %>%
  mutate(meanDiff.mean = mean(Diff.mean, na.rm=TRUE),
         sdDiff.mean = sd(Diff.mean, na.rm=TRUE),
         meanDiff.sd = mean(Diff.sd, na.rm=TRUE),
         sdDiff.sd = sd(Diff.sd, na.rm=TRUE),
         
         # code volumes above mean thresholds as trash
         upper.mean = meanDiff.mean + 2*sdDiff.mean,
         lower.mean = meanDiff.mean - 2*sdDiff.mean,
         trash.mean = ifelse(Diff.mean > upper.mean | Diff.mean < lower.mean, 1, 0),
         
         upper.sd = meanDiff.sd + 2*sdDiff.sd,
         lower.sd = meanDiff.sd - 2*sdDiff.sd,
         trash.sd = ifelse(Diff.sd > upper.sd | Diff.sd < lower.sd, 1, 0),
         
         # code volumes with more than +/- .25mm translation or rotation in Euclidian distance
         trash.rp.tr = ifelse(euclidian_trans_deriv > .25 | euclidian_trans_deriv < -.25, 1, 0),
         trash.rp.rot = ifelse(euclidian_rot_deriv > .25 | euclidian_rot_deriv < -.25, 1, 0)) %>%
  select(-meanDiff.mean, -meanDiff.sd, -sdDiff.mean, -sdDiff.sd) %>%
  
  # code trash based on striping
  group_by(subjectID, run, tile) %>%
  mutate(freqtile_power_c = freqtile_power - mean(freqtile_power, na.rm=TRUE)) %>%
  ungroup() %>%
  select(-freqtile_power) %>%
  spread(tile,freqtile_power_c) %>%
  mutate(trash.stripe = ifelse(tile_1 < -.035 & tile_10 > .00025, 1, 0)) %>%
  
  # combine trash
  mutate(trash.combined = ifelse(trash.stripe == 1, 1, 0),
         trash.sum = trash.rp.tr + trash.rp.rot + trash.mean + trash.sd,
         trash.combined = ifelse((trash.rp.tr + trash.rp.rot + trash.mean + trash.sd) > 1, 1, trash.combined)) %>%
  
  # recode as trash if volume behind and in front are both marked as trash
  mutate(trash.combined = ifelse(trash.combined == 0 & lag(trash.combined) == 1 & lead(trash.combined) == 1, 1, trash.combined)) %>%
         
  # code first volume as trash if second volume is trash
  mutate(trash.combined = ifelse(volume == 1 & lead(trash.combined) == 1, 1, trash.combined)) %>%

  # code hits
  mutate(hits = ifelse(trash.combined == 1 & (artifact == 1), "hit",
                ifelse(trash.combined == 0 & (artifact == 1), "neg",
                ifelse(trash.combined == 1 & (artifact == 0), "pos", NA))),
         label = ifelse(regexpr('.*', hits), as.character(volume), ''),
         hits = as.factor(hits)) %>%
  gather(tile, freqtile_power_c, c("tile_1", "tile_10"))

```

# compare hit rates
## training data
```{r}
# select only one set of observations and code correct rejections
train.tab = train.man %>% 
  filter(tile == "tile_1") %>%
  mutate(hits.tot = ifelse(hits %in% "hit", "hit",
                    ifelse(hits %in% "neg", "neg",
                    ifelse(hits %in% "pos", "pos",
                    ifelse(is.na(hits), "cor.rej", hits)))))
```

### lasso logistic regression
```{r}
confusionMatrix(pred_train, y_train)$table
confusionMatrix(pred_train, y_train)$overall[1]
confusionMatrix(pred_train, y_train)$byClass[11]
```

### svm
```{r}
confusionMatrix(train_pred, train.svm$artifact)$table
confusionMatrix(train_pred, train.svm$artifact)$overall[1]
confusionMatrix(train_pred, train.svm$artifact)$byClass[11]
```

### manual
```{r}
table(train.tab$hits.tot)

cor.rej = table(train.tab$hits.tot)[[1]]
hit = table(train.tab$hits.tot)[[2]]
neg = table(train.tab$hits.tot)[[3]]
pos = table(train.tab$hits.tot)[[4]]
total = cor.rej + hit + neg + pos

sprintf('Accuracy: %s', round((cor.rej + hit) / total,2))

# balanced accuracy
sprintf('Balanced accuracy: %s', round(((cor.rej / (cor.rej + pos)) + (hit / (hit + neg))) / 2,2))
```

## test data
```{r}
test.tab = test.man %>% 
  filter(tile == "tile_1") %>%
  mutate(hits.tot = ifelse(hits %in% "hit", "hit",
                    ifelse(hits %in% "neg", "neg",
                    ifelse(hits %in% "pos", "pos",
                    ifelse(is.na(hits), "cor.rej", NA)))))
```

### lasso logistic regression
```{r}
confusionMatrix(pred_test, y_test)$table
confusionMatrix(pred_test, y_test)$overall[1]
confusionMatrix(pred_test, y_test)$byClass[11]
```

### svm
```{r}
confusionMatrix(test_pred, test.svm$artifact)$table
confusionMatrix(test_pred, test.svm$artifact)$overall[1]
confusionMatrix(test_pred, test.svm$artifact)$byClass[11]
```

### manual 
```{r}
table(test.tab$hits.tot)

cor.rej = table(test.tab$hits.tot)[[1]]
hit = table(test.tab$hits.tot)[[2]]
neg = table(test.tab$hits.tot)[[3]]
pos = table(test.tab$hits.tot)[[4]]
total = cor.rej + hit + neg + pos

sprintf('Accuracy: %s', round((cor.rej + hit) / total,2))

# balanced accuracy
sprintf('Balanced accuracy: %s', round(((cor.rej / (cor.rej + pos)) + (hit / (hit + neg))) / 2,2))
```

# plot composite
## combine training and test data
```{r comp-translation, fig.width=20, fig.height=100}
full_man = bind_rows(train.man, test.man)
```

## logistic regression
```{r logreg-translation, fig.width=20, fig.height=100}
full_log = bind_rows(train.ml,test.ml)

# re-run lasso logistic regression on full sample
x = as.matrix(full_log[,-c(1,2,3,4)])
y = as.double(as.matrix(full_log[, 4]))
pred = predict(cv.train, newx = x, s=cv.train$lambda.1se, type="response")
pred[pred > .05] = 1
pred[pred < .05] = 0
confusionMatrix(pred, y)
```

## svm
```{r svm-translation, fig.width=20, fig.height=100}
full_svm = bind_rows(train.ml,test.ml)  %>%
  mutate(artifact = ifelse(artifact == 1, "yes","no"),
         artifact = as.factor(artifact))

# re-run svm on full sample
full_pred = predict(svmFit, newdata = full_svm, type="prob") %>%
  select(-no)
full_pred =  as.matrix(full_pred)
full_pred[full_pred > .09] = "yes"
full_pred[full_pred < .09] = "no"
confusionMatrix(full_pred, full_svm$artifact)
```

## manual
```{r}
full_man1 = full_man %>%
  filter(tile == "tile_1")
confusionMatrix(full_man1$trash.combined, full_man1$artifact)
```

# plot and compare models
```{r comp-models, fig.width=60, fig.height=100}
data.plot.log = bind_cols(full_log, as.data.frame(y), as.data.frame(pred)) %>%
  mutate(hits = ifelse(y == 1 & `1` == 1, "hit",
                ifelse(y == 0 & `1` == 1, "pos",
                ifelse(y == 1 & `1` == 0, "neg", NA))),
         label = ifelse(regexpr('.*', hits), as.character(volume), ''),
         hits = as.factor(hits))

data.plot.svm = bind_cols(full_svm, as.data.frame(full_pred)) %>%
  rename("full_pred" = yes) %>%
  mutate(hits = ifelse(artifact == "yes" & full_pred == "yes", "hit",
                ifelse(artifact == "no" & full_pred == "yes", "pos",
                ifelse(artifact == "yes" & full_pred == "no", "neg", NA))),
         label = ifelse(regexpr('.*', hits), as.character(volume), ''),
         hits = as.factor(hits))

plot.comp = full_man %>%
  filter(tile == "tile_1") %>%
  select(subjectID, run, volume, euclidian_trans_deriv, hits) %>%
  rename("auto" = hits) %>%
  left_join(data.plot.log, by = c("subjectID", "run", "volume", "euclidian_trans_deriv")) %>%
  select(subjectID, run, volume, euclidian_trans_deriv, auto, hits) %>%
  rename("log" = hits) %>%
  left_join(data.plot.svm, by = c("subjectID", "run", "volume", "euclidian_trans_deriv")) %>%
  select(subjectID, run, volume, euclidian_trans_deriv, auto, log, hits) %>%
  rename("svm" = hits) %>%
  gather(model, hits, c("auto", "log", "svm")) %>%
  mutate(label = ifelse(regexpr('.*', hits), as.character(volume), ''))

ggplot(plot.comp, aes(x = volume, y = euclidian_trans_deriv)) +
  geom_line(size = .25) +
  geom_point(data = subset(plot.comp, !is.na(hits)), aes(color = hits), size = 2.5) +
  geom_text(aes(label = label), size = 1.5) +
  facet_wrap(~ subjectID + run + model, ncol = 9, scales = "free") +
  scale_color_manual(values = c("#3B9AB2","#EBCC2A","#F21A00")) +
  theme(axis.text.x = element_text(size = 6))
```
